### 2016-11-09 paper/evaluation.tex
added balance and cpuness barplots
wip - research question 2

\newcommand{\RQB}{What is the distribution of CPU and IO bound
regression tests from the sample set?}

\newcommand{\RQC}{How uniformly distributed is the execution time
across test cases in costly projects?}

\newcommand{\RQD}{How often developers use the parallelism features
from build manager systems to improve performance on test execution?}

\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
\newcommand{\rqTwo}{\textbf{RQ2.} \RQC}
\newcommand{\rqThree}{\textbf{RQ3.} \RQB}
\newcommand{\rqFour}{\textbf{RQ4.} \RQD}

\begin{itemize}
    \item \rqOne
    \item \rqTwo
    \item \rqThree
    \item \rqFour
\end{itemize}

The first research question addresses the distribution of subjects per
time cost. We are interested on identifying time-consuming test suites
to investigate further their characteristics (\eg, type of application
and bottlenecks from execution) \Jbc{do we have a better arguments?}.
The second research question addresses the distribution of execution
time per test case. For each subject identified in the first research
question, we are interested in understanding how balanced is the cost
of the test suite in contrast to the cost of test cases and if there
are subjects where the time cost is mostly dominated by a small
fraction of test cases.

@@

\begin{itemize}
    \item \RQC
\end{itemize}

To evaluate the distribution of execution time, we calculated the cost
from 90\% of test cases ordered by execution time and compared the
resulting value to the total time.  We collected the elapsed time from
test cases for each generated report. Maven Surefire generates an XML
report with execution information (\eg, number of skipped tests and
elapsed time) per test suite \Jbc{Should I use the previous sentence
as a footnote or should I delete it?}. We noticed that some test cases
reported an elapsed time of zero: since the reported time is in
milliseconds, some tests may execute in a shorter time. \Fix{..to be
continued...}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.4\textwidth]{figs/tcdistrib.pdf}
    \caption{\Fix{...}}
\end{figure}

\subsection{Answering research question RQ3}
\label{sec:rqThree}

@@

To evaluate the distribution of CPU and IO bound in regression tests
from the sample set, we proposed the definition of \emph{cpuness}
computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
where \emph{user\_t} is the elapsed time of execution in \emph{user
mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
\emph{elapsed\_t} is the elapsed time to finish the execution. We
measured the \emph{cpuness} of each regression test \Fix{...elaborate
the meaning of cpuness} \Fix{Describe how I measured user, system and
"wall" time}.  \Fix{Explain results}.  \Fix{show plots}

\subsection{Answering research question RQ4}
\label{sec:rqfour}

%% \begin{itemize}
%%     \item \RQFOUR
%% \end{itemize}

\Fix{to appear...}

>>>>

\newcommand{\RQB}{How often do developers use low-level parallelism
to improve runtime performance?}

%%\newcommand{\RQB}{What is the distribution of CPU and IO bound
%%regression test suites from the sample set?}
%%
%%\newcommand{\RQC}{How uniformly distributed is the execution time
%%across test cases in costly projects?}
%%
%%\newcommand{\RQD}{How often developers use the parallelism features
%%from build systems to improve runtime performance?}

\newcommand{\rqOne}{\textbf{RQ1.} \RQA}
\newcommand{\rqTwo}{\textbf{RQ2.} \RQB}
%%\newcommand{\rqThree}{\textbf{RQ3.} \RQB}
%%\newcommand{\rqFour}{\textbf{RQ4.} \RQD}

\begin{itemize}
    \item \rqOne
    \item \rqTwo
\end{itemize}

The first research question addresses the distribution of subjects per
time cost. We are interested on identifying time-consuming test suites
to investigate further their characteristics (\eg, type of application
and bottlenecks from execution) \Jbc{do we have more arguments?}.  The
second research question addresses our interest in understanding if
developers are aware of parallelism features from testing frameworks
available out-of-the-box through build systems (\eg, JUnit and TestNG
with Maven Surefire) and what setting are often used.

\Fix{distribution of execution
    time per test case. For each subject identified in the first
    research question, we investigate how balanced is the cost of the
    test suite in contrast to the cost of test cases and if there are
    subjects where the time cost is mostly dominated by a small
fraction of test cases.} \Fix{The third research question addresses
    the distribution of regression tests according to the use of
    computational resources.  We are interested in investigating if
regression test suites are CPU intensive and if there are
opportunities to improve performance. The RQ4 addresses}
\Fix{...elaborate...}

@@

@@

To evaluate how often developers use low-level parallelism, we
considered 216 Maven projects and analyzed \Fix{x} configurations
files. \Fix{For each subject, we parsed all \emph{pom.xml} files from the
project (including submodules) and searched for all \emph{surefire}
settings on each XML file. Figure \Fix{...} illustrates how a
developer can explore parallelism via Surefire settings.}

\begin{center}
\lstset{language=XML}
\begin{lstlisting}
 <plugin>
     <groupId>org.apache.maven.plugins</groupId>
     <artifactId>maven-surefire-plugin</artifactId>
     <configuration>
         <parallel>methods</parallel>
         <threadCount>2</threadCount>
         <perCoreThreadCount>true</perCoreThreadCount>
     </configuration>
</plugin>
\caption{\Fix{...}}
\end{lstlisting}
\label{code:surefire}
\end{center}

\begin{figure}[h!]
   \centering
   \includegraphics[width=0.4\textwidth]{results/plots/parallelism-settings.pdf}
   \caption{\Fix{...}}
\end{figure}

%%To evaluate the distribution of execution time per project, we sorted
%%the test cases by decreasing order of elapsed time and calculated the
%%number of tests executed in 90\% of the total time. Later, we reported
%%the \Fix{balance} of execution time by dividing the number of tests
%%that represents 90\% of the execution time by the number of tests
%%cases. For instance, a balance of 50\% indicates \Fix{...}.  \Fix{We
%%collected the elapsed time from test cases for each generated report.
%%Maven Surefire generates an XML report with execution information
%%(\eg, number of skipped tests and elapsed time) per test suite
%%\Jbc{Should I use the previous sentence as a footnote or should I
%%delete it?}. We noticed that some test cases reported an elapsed time
%%of zero: since the reported time is in milliseconds, some tests may
%%execute in a shorter time. \Fix{..to be continued...}}. Results
%%indicate that \Fix{...}.
%%
%%\begin{figure}[h!]
%%    \centering
%%    \includegraphics[width=0.4\textwidth]{results/plots/balance.pdf}
%%    \caption{\Fix{balance}}
%%\end{figure}

%% \subsection{Answering research question RQ3}
%% \label{sec:rqThree}
%% 
%% \begin{itemize}
%%     \item \RQB
%% \end{itemize}
%% 
%% To evaluate the distribution of CPU and IO intensive test suites from
%% the sample set, we used the command \emph{sar} to monitor the system
%% activity in background while tests ran. \emph{Sar} is a command that
%% collects and reports statistics (\eg, percentage of IO waiting and
%% usage of CPU in user mode) based on the kernel activity and it is
%% highly configurable to collect detailed information (\eg, usage of a
%% specific processor core or percentage of network interface
%% utilization). We configured \emph{sar} to report \Fix{...explain how
%% we executed and what fields we are interested}. \Fix{explain fields}.
%% Figure \Fix{A} shows the distribution of subjects grouped in intervals
%% of \Fix{W}\% of CPU utilization. Results indicates that \Fix{...}
%% 
%% \begin{figure}[h!]
%%     \centering
%%     \includegraphics[width=0.4\textwidth]{results/plots/cpuness.pdf}
%%     \caption{\Fix{cpu usage}}
%% \end{figure}
%% 
%% \Comment{we proposed the definition of \emph{cpuness}
%% computed as the follow: $((user\_t + system\_t) / elapsed\_t) * 100$,
%% where \emph{user\_t} is the elapsed time of execution in \emph{user
%% mode}, \emph{system\_t} is the elapsed in \emph{kernel mode}, and
%% \emph{elapsed\_t} is the elapsed time to finish the execution. We
%% measured the \emph{cpuness} of each regression test \Fix{...elaborate
%% the meaning of cpuness} \Fix{Describe how I measured user, system and
%% "wall" time}.  \Fix{Explain results}.  \Fix{show plots}}
%% 
%% \subsection{Answering research question RQ4}
%% \label{sec:rqfour}
%% 
%% \begin{itemize}
%%     \item \RQD
%% \end{itemize}
%% 
%% \Fix{to appear...}
%%
